|

### 2024-08-20 reproducibility/manuscript/manuscript.qmd
docs(manuscript): factor format-specific settings
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: |
  Pyro&thinsp;-Velocity: Probabilistic RNA Velocity inference from single-cell data
number-sections: true
toc: true
toc-title: Contents
format:
  nature-pdf:
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-nature
    classoption: 
      - lineno
    # `citeproc` is the pandoc default. Set `cite-method: natbib` if required
    # to use the bst styles from the upstream template.
    cite-method: natbib
    keep-tex: true
    equal-margins: false
    include-in-header: header.tex
    link-citations: true
  html:
    code-fold: true
    html-math-method: mathjax
  docx:
    reference-doc: styles.docx
# filters:
#   - authors-block
csl: _extensions/sciexp/nature/csl/springer-basic-brackets-no-et-al.csl
affiliations:
  - name: Massachusetts General Hospital Research Institute, Charlestown, MA
    id: 1
    department: Molecular Pathology Unit
    city: Charlestown
    state: MA
    postal-code: 02129
  - name: Harvard Medical School, Charlestown, MA
    id: 2
    department: Massachusetts General Hospital Cancer Center
    city: Charlestown
    state: MA
    postal-code: 02129
  - name: Massachusetts General Hospital, Boston, MA
    id: 3
    department: Center for Regenerative Medicine
    city: Boston
    state: MA
    postal-code: 02114
  - name: Harvard University, Cambridge, MA
    id: 4
    department: Harvard Stem Cell Institute
    city: Cambridge
    state: MA
    postal-code: 02139
  - name: Cambridge, MA
    id: 5
    department: Broad Institute of MIT and Harvard
    city: Cambridge
    state: MA
    postal-code: 02142
  - name: Laboratory of Neurodevelopmental Systems Biology, Lausanne, Switzerland
    id: 6
    department: |
      Brain and Mind Institute, School of Life Sciences, 
      École Polytechnique Fédérale de Lausanne (EPFL)
    city: Lausanne
    state: Switzerland
    postal-code: 1015
  - name: Cambridge, MA
    id: 7
    department: Basis Research Institute
    city: Cambridge
    state: MA
    postal-code: 02142
authors:
  - name: Qian Qin
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
      - ref: 5
    # attributes:
    #   equal-contributor: true
  - name: Eli Bingham
    affiliations:
      - ref: 5
      - ref: 7
  - name: Gioele La Manno
    affiliations:
      - ref: 6
    email: gioele.lamanno@epfl.ch
    attributes:
      corresponding: true
  - name: David M. Langenau
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
    email: dlangenau@mgh.harvard.edu
    attributes:
      corresponding: true
  - name: Luca Pinello
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 5
    email: lpinello@mgh.harvard.edu
    attributes:
      corresponding: true
abstract: |
  Single-cell RNA Velocity has dramatically advanced our ability to model
  cellular differentiation and cell fate decisions. However, current
  preprocessing choices and model assumptions often lead to errors in assigning
  developmental trajectories. Here, we develop, Pyro-Velocity, a Bayesian,
  generative, and multivariate RNA Velocity model to estimate the uncertainty of
  cell future states. This approach models raw sequencing counts with the
  synchronized cell time across all expressed genes to provide quantifiable and
  improved information on cell fate choices and developmental trajectory
  dynamics.
keywords: [
  RNA velocity, 
  single-cell RNA sequencing, 
  probabilistic generative modeling, 
  cell fate, 
  developmental trajectory inference
]
bibliography: bibliography.bib
crossref:
  fig-prefix: Fig.
  custom:
    - kind: float
      key: suppfig
      latex-env: suppfig
      reference-prefix: Fig. S
      space-before-numbering: false
      latex-list-of-description: Supplementary Figure
---

>>>>

---
title: |
  Pyro&thinsp;-Velocity: Probabilistic RNA Velocity inference from single-cell data
format:
  nature-pdf:
    # journal.cite-style is included in the tex file but ignored by pandoc if 
    # cite-method is not `natbib`.
    journal:
      cite-style: sn-mathphys-num
    classoption: 
      - lineno
    cite-method: natbib
    link-citations: true
    toc: true
    toc-title: Contents
    number-sections: true
    keep-tex: true
    equal-margins: false
    include-in-header: header.tex
  html:
    code-fold: true
    html-math-method: mathjax
  docx:
    reference-doc: styles.docx
    cite-method: citeproc
    filters:
      - authors-block
csl: _extensions/sciexp/nature/csl/springer-basic-brackets-no-et-al.csl
affiliations:
  - name: Massachusetts General Hospital Research Institute, Charlestown, MA
    id: 1
    department: Molecular Pathology Unit
    city: Charlestown
    state: MA
    postal-code: 02129
  - name: Harvard Medical School, Charlestown, MA
    id: 2
    department: Massachusetts General Hospital Cancer Center
    city: Charlestown
    state: MA
    postal-code: 02129
  - name: Massachusetts General Hospital, Boston, MA
    id: 3
    department: Center for Regenerative Medicine
    city: Boston
    state: MA
    postal-code: 02114
  - name: Harvard University, Cambridge, MA
    id: 4
    department: Harvard Stem Cell Institute
    city: Cambridge
    state: MA
    postal-code: 02139
  - name: Cambridge, MA
    id: 5
    department: Broad Institute of MIT and Harvard
    city: Cambridge
    state: MA
    postal-code: 02142
  - name: Laboratory of Neurodevelopmental Systems Biology, Lausanne, Switzerland
    id: 6
    department: |
      Brain and Mind Institute, School of Life Sciences, 
      École Polytechnique Fédérale de Lausanne (EPFL)
    city: Lausanne
    state: Switzerland
    postal-code: 1015
  - name: Cambridge, MA
    id: 7
    department: Basis Research Institute
    city: Cambridge
    state: MA
    postal-code: 02142
authors:
  - name: Qian Qin
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
      - ref: 5
    # attributes:
    #   equal-contributor: true
  - name: Eli Bingham
    affiliations:
      - ref: 5
      - ref: 7
  - name: Gioele La Manno
    affiliations:
      - ref: 6
    email: gioele.lamanno@epfl.ch
    attributes:
      corresponding: true
  - name: David M. Langenau
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
      - ref: 4
    email: dlangenau@mgh.harvard.edu
    attributes:
      corresponding: true
  - name: Luca Pinello
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 5
    email: lpinello@mgh.harvard.edu
    attributes:
      corresponding: true
abstract: |
  Single-cell RNA Velocity has dramatically advanced our ability to model
  cellular differentiation and cell fate decisions. However, current
  preprocessing choices and model assumptions often lead to errors in assigning
  developmental trajectories. Here, we develop, Pyro-Velocity, a Bayesian,
  generative, and multivariate RNA Velocity model to estimate the uncertainty of
  cell future states. This approach models raw sequencing counts with the
  synchronized cell time across all expressed genes to provide quantifiable and
  improved information on cell fate choices and developmental trajectory
  dynamics.
keywords: [
  RNA velocity, 
  single-cell RNA sequencing, 
  probabilistic generative modeling, 
  cell fate, 
  developmental trajectory inference
]
bibliography: bibliography.bib
crossref:
  fig-prefix: Fig.
  custom:
    - kind: float
      key: suppfig
      latex-env: suppfig
      reference-prefix: Fig. S
      space-before-numbering: false
      latex-list-of-description: Supplementary Figure
---
